Squintability and Other Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimisation Choices

### 2025-03-02 jso.qmd
add references to pkgs used in the work

```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(ggplot2)
library(patchwork)
library(ggh4x)
library(broom)
library(kableExtra)
library(tourr)
library(PPtreeViz)
library(ferrn)
library(colorspace)
library(broom)
load(here::here("data/sim_pipe_run_best.rda"))
load(here::here("data/sim_sine_6d_spline_head.rda"))
load(here::here("data/sim_sine_6d_spline_best.rda"))
load(here::here("data/sim_sine_6d_spline_projdist.rda"))
load(here::here("data/pipe_better.rda"))
load(here::here("data/pipe_jellyfish.rda"))
load(here::here("data/smoothness.rda"))
load(here::here("data/squintability.rda"))
load(here::here("data/sq_basis_dist_idx.rda"))
load(here::here("data/sim_df.rda"))
```

@@

```{r}
#| label: tbl-smoothness-squintability
#| tbl-cap: Parameters estimated from the Gaussian process (outputscale $\eta$, lengthscale $\ell$, smoothness $\nu$, and nugget $\sigma$) and scaled logistic function ($\theta_1$ to $\theta_4$ and $\varsigma$) for the pipe-finding and sine-wave finding problems.  The columns $\nu$ and $\varsigma$ represent the smoothness and squintability measures respectively.
dt <- tibble(shape = c(rep("pipe", 4), rep("sine", 18)), smoothness) |>
  left_join(squintability) |> 
  rename(d = n, smooth = smoothness) |> 
  mutate(index = ifelse(index == "dcor2d_2", "dcor", index),
         index = ifelse(index == "loess2d", "loess", index),
         index = ifelse(index == "splines2d", "splines", index),
         variance = sqrt(variance)) 
dt |> 
  knitr::kable(
    digits = 2, format = "latex", 
    col.names = c(
      "shape", "index", "d",
      "$\\eta$", "$\\ell$", "$\\nu$", "$\\sigma$",
      "$\\theta_1$", "$\\theta_2$", "$\\theta_3$", "$\\theta_4$", "$\\varsigma$"), linesep = "",
    booktabs = TRUE, escape = FALSE, row.names = FALSE, align = "|llr|rrrr|rrrrr") |> 
  #column_spec(1, border_left = TRUE) |> 
  #column_spec(c(4, 8, 13), border_right = TRUE) |> 
  kable_styling(font_size = 10) 
```

@@

>>>>

```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(patchwork)
library(ggh4x)
library(broom)
library(kableExtra)
library(tourr)
library(ferrn)
load(here::here("data/sim_pipe_run_best.rda"))
load(here::here("data/sim_sine_6d_spline_head.rda"))
load(here::here("data/sim_sine_6d_spline_best.rda"))
load(here::here("data/sim_sine_6d_spline_projdist.rda"))
load(here::here("data/pipe_better.rda"))
load(here::here("data/pipe_jellyfish.rda"))
load(here::here("data/smoothness.rda"))
load(here::here("data/squintability.rda"))
load(here::here("data/sq_basis_dist_idx.rda"))
load(here::here("data/sim_df.rda"))
```

@@

```{r}
#| label: tbl-smoothness-squintability
#| tbl-cap: Parameters estimated from the Gaussian process (outputscale $\eta$, lengthscale $\ell$, smoothness $\nu$, and nugget $\sigma$) and scaled logistic function ($\theta_1$ to $\theta_4$ and $\varsigma$) for the pipe-finding and sine-wave finding problems.  The columns $\nu$ and $\varsigma$ represent the smoothness and squintability measures respectively.
dt <- tibble(shape = c(rep("pipe", 5), rep("sine", 17)), smoothness) |>
  left_join(squintability) |> 
  rename(d = n, smooth = smoothness) |> 
  mutate(index = ifelse(index == "dcor2d_2", "dcor", index),
         index = ifelse(index == "loess2d", "loess", index),
         index = ifelse(index == "splines2d", "splines", index),
         variance = sqrt(variance)) 
dt |> 
  knitr::kable(
    digits = 2, format = "latex", 
    col.names = c(
      "shape", "index", "d",
      "$\\eta$", "$\\ell$", "$\\nu$", "$\\sigma$",
      "$\\theta_1$", "$\\theta_2$", "$\\theta_3$", "$\\theta_4$", "$\\varsigma$"), linesep = "",
    booktabs = TRUE, escape = FALSE, row.names = FALSE, align = "|llr|rrrr|rrrrr") |> 
  #column_spec(1, border_left = TRUE) |> 
  #column_spec(c(4, 8, 13), border_right = TRUE) |> 
  kable_styling(font_size = 10) 
```

@@

The R packages used in this work include: `tidyverse` [@tidyverse]; 
`patchwork` [@patchwork]; `ggh4x` [@ggh4x]; `broom` [@broom]; 
`kableExtra` [@kabelextra]; `ferrn` [@RJ-2021-105]; and `cassowaryr` [@cassowaryr].

### 2025-03-02 jso.tex
add references to pkgs used in the work

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{orcidlink}
\usepackage{algorithm}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\theoremstyle{plain}
\newtheorem{defn}{\protect\definitionname}
\newtheorem{prop}{\protect\propositionname}
\providecommand{\definitionname}{Definition}
\providecommand{\propositionname}{Proposition}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

Optimisation of PP is often discussed when new indexes are proposed
(Posse 1995; Marie-Sainte, Berro, and Ruiz-Gazen 2010; Grochowski and
Duch 2011). Cook et al. (1995) tied the optimisation more closely to the
index, when they introduced the PPGT, which monitors the optimisation
visually so that the user can see the projected data leading in and out
of the optimum. An implementation is available in the \texttt{tourr}
package (Wickham et al. 2011) in R (R Core Team 2023). Zhang et al.
(2021) illustrated how to diagnose optimisation processes, particularly
focusing on the guided tour, and revealed a need for improved
optimisation. While improving the quality of the optimisation solutions
in the tour is essential, it is also important to be able to view the
data projections as the optimisation progresses. Integrating the guided
tour with a global optimisation algorithm that is efficient in finding
the global optimal and enables viewing of the projected data during the
exploration process is a goal.

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, colback=white, opacityback=0, coltitle=black, title={Algorithm: Jellyfish Optimizer Pseudo Code}, leftrule=.75mm, breakable, arc=.35mm, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, bottomrule=.15mm, toprule=.15mm, rightrule=.15mm, titlerule=0mm]

@@

\begin{tabular}{|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr}
\toprule
shape & index & d & $\eta$ & $\ell$ & $\nu$ & $\sigma$ & $\theta_1$ & $\theta_2$ & $\theta_3$ & $\theta_4$ & $\varsigma$\\
\midrule
pipe & holes & 4 & 0.03 & 0.36 & 2.99 & 0.00 & 1.00 & 0.78 & 4.50 & 0.03 & 0.31\\
pipe & holes & 6 & 0.03 & 0.38 & 3.09 & 0.00 & 1.02 & 0.86 & 3.37 & 0.02 & 0.41\\
pipe & holes & 8 & 0.02 & 0.33 & 2.90 & 0.00 & 1.01 & 0.87 & 3.26 & 0.03 & 0.41\\
pipe & holes & 10 & 0.02 & 0.34 & 2.88 & 0.00 & 1.02 & 0.88 & 3.15 & 0.02 & 0.43\\
sine & holes & 12 & 0.02 & 0.43 & 2.72 & 0.00 & 1.01 & 0.88 & 3.34 & 0.00 & 0.41\\
sine & MIC & 4 & 0.14 & 0.27 & 3.56 & 0.00 & 0.94 & 0.15 & 1.14 & -0.04 & 0.39\\
sine & MIC & 6 & 0.06 & 0.31 & 3.08 & 0.00 & 0.89 & 0.57 & 1.62 & -0.03 & 0.39\\
sine & MIC & 8 & 0.03 & 0.32 & 2.75 & 0.00 & 0.93 & 0.33 & 1.31 & -0.04 & 0.38\\
sine & TIC & 4 & 0.40 & 0.27 & 3.49 & 0.00 & 0.97 & 0.46 & 1.55 & -0.04 & 0.38\\
sine & TIC & 6 & 0.16 & 0.31 & 3.08 & 0.00 & 0.95 & 0.54 & 1.72 & -0.03 & 0.37\\
sine & TIC & 8 & 0.07 & 0.30 & 2.72 & 0.00 & 0.95 & 0.56 & 1.72 & -0.03 & 0.38\\
sine & dcor & 4 & 0.22 & 0.30 & 3.63 & 0.00 & 0.96 & 1.07 & 2.67 & -0.03 & 0.56\\
sine & dcor & 6 & 0.08 & 0.29 & 3.13 & 0.00 & 0.95 & 1.04 & 2.74 & -0.03 & 0.53\\
sine & loess & 4 & 0.34 & 0.50 & 2.90 & 0.00 & 1.02 & 1.10 & 2.50 & 0.05 & 0.57\\
sine & loess & 6 & 0.24 & 0.46 & 3.56 & 0.00 & 1.02 & 1.04 & 2.65 & 0.07 & 0.53\\
sine & loess & 8 & 0.19 & 0.46 & 3.36 & 0.00 & 1.02 & 1.04 & 2.62 & 0.08 & 0.53\\
sine & skinny & 6 & 0.05 & 0.19 & 2.24 & 0.01 & 0.83 & 0.00 & 2.98 & 0.05 & 0.10\\
sine & splines & 4 & 0.24 & 0.32 & 3.55 & 0.00 & 1.01 & 1.09 & 2.65 & -0.03 & 0.57\\
sine & splines & 6 & 0.10 & 0.32 & 3.11 & 0.00 & 1.01 & 1.05 & 2.73 & -0.02 & 0.54\\
sine & splines & 8 & 0.05 & 0.29 & 2.74 & 0.00 & 1.02 & 1.06 & 2.68 & -0.02 & 0.54\\
sine & stringy2 & 4 & 0.02 & 0.30 & 2.76 & 1.01 & 0.64 & 0.05 & 7.89 & 0.05 & 0.00\\
sine & stringy2 & 6 & 0.02 & 0.07 & 1.51 & 0.05 & 0.65 & 0.05 & 7.78 & 0.06 & 0.00\\
\bottomrule
\end{tabular}
\endgroup{}

@@

\setlength{\LTpost}{0mm}

@@

\toprule
\textbf{Characteristic} & \textbf{OR} \textbf{(95\% CI)}\textsuperscript{\textit{1}} & \textbf{p-value} \\ 
\midrule\addlinespace[2.5pt]
Smoothness & 1.00 (0.90 to 1.11) & 0.928 \\ 
Squintability & 1.24 (1.13 to 1.39) & \textbf{<0.001} \\ 
Dimension & 0.57 (0.44 to 0.73) & \textbf{<0.001} \\ 
Number of jellyfish & 1.32 (1.17 to 1.50) & \textbf{<0.001} \\ 
Maximum number of tries & 1.06 (0.94 to 1.21) & 0.333 \\ 
\bottomrule

@@

@@

@@

@@

@@

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{anyfontsize}
\usepackage{orcidlink}
\usepackage{algorithm}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\theoremstyle{plain}
\newtheorem{defn}{\protect\definitionname}
\newtheorem{prop}{\protect\propositionname}
\providecommand{\definitionname}{Definition}
\providecommand{\propositionname}{Proposition}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

Optimisation of PP is often discussed when new indexes are proposed
(Posse 1995; Marie-Sainte, Berro, and Ruiz-Gazen 2010; Grochowski and
Duch 2011). Cook et al. (1995) tied the optimisation more closely to the
index, when they introduced the PPGT, which monitors the optimisation
visually so that the user can see the projected data leading in and out
of the optimum. An implementation is available in the \texttt{tourr}
package (H. Wickham et al. 2011) in R (R Core Team 2023). Zhang et al.
(2021) illustrated how to diagnose optimisation processes, particularly
focusing on the guided tour, and revealed a need for improved
optimisation. While improving the quality of the optimisation solutions
in the tour is essential, it is also important to be able to view the
data projections as the optimisation progresses. Integrating the guided
tour with a global optimisation algorithm that is efficient in finding
the global optimal and enables viewing of the projected data during the
exploration process is a goal.

@@

\begin{tcolorbox}[enhanced jigsaw, breakable, toprule=.15mm, titlerule=0mm, coltitle=black, left=2mm, arc=.35mm, colbacktitle=quarto-callout-note-color!10!white, colback=white, rightrule=.15mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, toptitle=1mm, opacityback=0, colframe=quarto-callout-note-color-frame, leftrule=.75mm, bottomtitle=1mm, bottomrule=.15mm, opacitybacktitle=0.6]

@@

\begin{tabular}{|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr}
\toprule
shape & index & d & $\eta$ & $\ell$ & $\nu$ & $\sigma$ & $\theta_1$ & $\theta_2$ & $\theta_3$ & $\theta_4$ & $\varsigma$\\
\midrule
pipe & holes & 4 & 0.03 & 0.36 & 2.99 & 0.00 & 1.00 & 0.78 & 4.50 & 0.03 & 0.31\\
pipe & holes & 6 & 0.03 & 0.38 & 3.09 & 0.00 & 1.02 & 0.86 & 3.37 & 0.02 & 0.41\\
pipe & holes & 8 & 0.02 & 0.33 & 2.90 & 0.00 & 1.01 & 0.87 & 3.26 & 0.03 & 0.41\\
pipe & holes & 10 & 0.02 & 0.34 & 2.88 & 0.00 & 1.02 & 0.88 & 3.15 & 0.02 & 0.43\\
pipe & holes & 12 & 0.02 & 0.43 & 2.72 & 0.00 & 1.01 & 0.88 & 3.34 & 0.00 & 0.41\\
sine & MIC & 4 & 0.14 & 0.27 & 3.56 & 0.00 & 0.94 & 0.15 & 1.14 & -0.04 & 0.39\\
sine & MIC & 6 & 0.06 & 0.31 & 3.08 & 0.00 & 0.89 & 0.57 & 1.62 & -0.03 & 0.39\\
sine & MIC & 8 & 0.03 & 0.32 & 2.75 & 0.00 & 0.93 & 0.33 & 1.31 & -0.04 & 0.38\\
sine & TIC & 4 & 0.40 & 0.27 & 3.49 & 0.00 & 0.97 & 0.46 & 1.55 & -0.04 & 0.38\\
sine & TIC & 6 & 0.16 & 0.31 & 3.08 & 0.00 & 0.95 & 0.54 & 1.72 & -0.03 & 0.37\\
sine & TIC & 8 & 0.07 & 0.30 & 2.72 & 0.00 & 0.95 & 0.56 & 1.72 & -0.03 & 0.38\\
sine & dcor & 4 & 0.22 & 0.30 & 3.63 & 0.00 & 0.96 & 1.07 & 2.67 & -0.03 & 0.56\\
sine & dcor & 6 & 0.08 & 0.29 & 3.13 & 0.00 & 0.95 & 1.04 & 2.74 & -0.03 & 0.53\\
sine & loess & 4 & 0.34 & 0.50 & 2.90 & 0.00 & 1.02 & 1.10 & 2.50 & 0.05 & 0.57\\
sine & loess & 6 & 0.24 & 0.46 & 3.56 & 0.00 & 1.02 & 1.04 & 2.65 & 0.07 & 0.53\\
sine & loess & 8 & 0.19 & 0.46 & 3.36 & 0.00 & 1.02 & 1.04 & 2.62 & 0.08 & 0.53\\
sine & skinny & 6 & 0.05 & 0.19 & 2.24 & 0.01 & 0.83 & 0.00 & 2.98 & 0.05 & 0.10\\
sine & splines & 4 & 0.24 & 0.32 & 3.55 & 0.00 & 1.01 & 1.09 & 2.65 & -0.03 & 0.57\\
sine & splines & 6 & 0.10 & 0.32 & 3.11 & 0.00 & 1.01 & 1.05 & 2.73 & -0.02 & 0.54\\
sine & splines & 8 & 0.05 & 0.29 & 2.74 & 0.00 & 1.02 & 1.06 & 2.68 & -0.02 & 0.54\\
sine & stringy2 & 4 & 0.02 & 0.30 & 2.76 & 1.01 & 0.64 & 0.05 & 7.89 & 0.05 & 0.00\\
sine & stringy2 & 6 & 0.02 & 0.07 & 1.51 & 0.05 & 0.65 & 0.05 & 7.78 & 0.06 & 0.00\\
\bottomrule
\end{tabular}
\endgroup{}

@@

\begingroup
\fontsize{12.0pt}{14.4pt}\selectfont
\setlength{\LTpost}{0mm}

@@

\toprule
\textbf{Characteristic} & \textbf{OR} \textbf{(95\% CI)}\textsuperscript{\textit{1}} & \textbf{p-value} \\ 
\midrule\addlinespace[2.5pt]
Smoothness & 1.00 (0.90 to 1.11) & 0.928 \\ 
Squintability & 1.24 (1.13 to 1.39) & {\bfseries <0.001} \\ 
Dimension & 0.57 (0.44 to 0.73) & {\bfseries <0.001} \\ 
Number of jellyfish & 1.32 (1.17 to 1.50) & {\bfseries <0.001} \\ 
Maximum number of tries & 1.06 (0.94 to 1.21) & 0.333 \\ 
\bottomrule

@@

The R packages used in this work include: \texttt{tidyverse} (Hadley
Wickham et al. 2019); \texttt{patchwork} (Pedersen 2024); \texttt{ggh4x}
(van den Brand 2024); \texttt{broom} (Robinson, Hayes, and Couch 2024);
\texttt{kableExtra} (Zhu 2024); \texttt{ferrn} (Zhang et al. 2021); and
\texttt{cassowaryr} (Mason et al. 2022).

@@

\bibitem[\citeproctext]{ref-cassowaryr}
Mason, Harriet, Stuart Lee, Ursula Laa, and Dianne Cook. 2022.
\emph{Cassowaryr: Compute Scagnostics on Pairs of Numeric Variables in a
Data Set}. \url{https://CRAN.R-project.org/package=cassowayr}.

\bibitem[\citeproctext]{ref-patchwork}
Pedersen, Thomas Lin. 2024. \emph{Patchwork: The Composer of Plots}.
\url{https://CRAN.R-project.org/package=patchwork}.

@@

\bibitem[\citeproctext]{ref-broom}
Robinson, David, Alex Hayes, and Simon Couch. 2024. \emph{Broom: Convert
Statistical Objects into Tidy Tibbles}.
\url{https://CRAN.R-project.org/package=broom}.

@@

\bibitem[\citeproctext]{ref-ggh4x}
van den Brand, Teun. 2024. \emph{Ggh4x: Hacks for 'Ggplot2'}.
\url{https://CRAN.R-project.org/package=ggh4x}.

\bibitem[\citeproctext]{ref-tidyverse}
Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.

@@

\bibitem[\citeproctext]{ref-kabelextra}
Zhu, Hao. 2024. \emph{kableExtra: Construct Complex Table with 'Kable'
and Pipe Syntax}. \url{https://CRAN.R-project.org/package=kableExtra}.
